---
title: "Data Vizes in TS"
execute:
  echo: false
---

# Problem 1:
```{r}
#| output: false
library(ggplot2)
library(lubridate)
library(tidyverse)
library(quantmod)
library(tidyquant)
library(plotly)
```

```{r}
#| output: false
options("getSymbols.warning4.0"=FALSE)
options("getSymbols.yahoo.warning"=FALSE)

tickers = c("NKE","CHDRY","ROST", "ADDYY", "PUMSY","HNNMY")
for (i in tickers){
  getSymbols(i, from = "2020-01-01", to = "2023-05-01")}

x <- list(
  title = "date"
)

y <- list(
  title = "value"
)

stock <- data.frame(NKE$NKE.Adjusted,
                    CHDRY$CHDRY.Adjusted,
                    ROST$ROST.Adjusted,
                    ADDYY$ADDYY.Adjusted,
                    PUMSY$PUMSY.Adjusted,
                    HNNMY$HNNMY.Adjusted)


stock <- data.frame(stock,rownames(stock))
colnames(stock) <- append(tickers,'Dates')
head(stock)

stock$Dates<-as.Date(stock$Dates,"%Y-%m-%d")
```

This plot depicts the stock prices for large fashion companies pre and post the COVID-19 pandemic. The fashion brands included are Adidas, Christian Dior, H&M, Nike, Puma, and Ross. Looking a combination of high end and low end brands, we can see that all companies faced a massive downtick in price evaluations in March of 2020, signaling the announcement of the global COVID-19 pandemic. Something to point out is that Christian Dior had a spike in price around mid-2021, resulting in a high uptick compared to the other brands. I was unable to find a reason as to why this uptick occured, but we can assume it was due to the highend nature of the brand. 

```{r}
# place your ggplotly visualization here
ggplot(stock, aes(x=Dates)) +
  geom_line(aes(y=NKE, colour="NKE"))+
  geom_line(aes(y=CHDRY, colour="CHDRY"))+
  geom_line(aes(y=ROST, colour="ROST"))+
  geom_line(aes(y=ADDYY, colour="ADDYY"))+
  geom_line(aes(y=PUMSY, colour="PUMSY"))+
  geom_line(aes(y=HNNMY, colour="HNNMY"))+
   labs(
    title = "Stock Prices for Large Fashion Companies pre/post Pandemic",
    subtitle = "From 2020-2023",
    x = "Date",
    y = "Adjusted Closing Prices")+
    theme(panel.background = element_rect(fill = "white", colour = "grey50"))+
    guides(colour=guide_legend(title="Fashion Companies")) 
```

# Problem 2: 
The following graph depicts the precipication in Washington D.C. from January 2021 - January 2022. The graph shows periodic spikes throughout the year, however, the most precipitation occured in the third quarter of the year, with the highest amount occuring on August 20, 2021 at 3.76. The driest part of the year was the last quarter. 

```{r}
climate <- read.csv("climate.csv")

climate$DATE <- as.Date(climate$DATE,"%Y-%m-%d")
g2<- climate %>%
  ggplot(aes(y= PRCP, x= DATE))+
  geom_line(color="lightblue")+
  scale_x_date(date_labels = "%B/%Y") +
  labs(
    title = "Precipitation in Washington D.C. - Time Series",
    x = "Time",
    y = "Precipitation")

ggplotly(g2)
```


# Problem 3: 
Below, is a graph depicting the unemployement rate for women in the United States of America throughout the 2000's. This data was sourced from [FRED](https://fred.stlouisfed.org/series/LNS14000002). From this graph we can see 2 major historical moments that caused women's unemployement. The 2008 market crash caused the first steep incline in unemployment. However, the market was able to recover such that the women who did work were able to in the 2010's. The next major event was the COVID-19 global pandemic. Due to a global shutdown, there was a major spike in unemployement. This may be due to several women also being mothers and needing to stay home for childcare as a result of childcare services being unavailable at the time. 

```{r}
#| warning: false
unemployement <- read.csv("unemployement.csv")
unemployement$DATE <- as.Date(unemployement$DATE,"%Y-%m-%d")

fig <- plot_ly(unemployement, type = 'scatter', mode = 'lines')%>%
  add_trace(x = ~DATE, y = ~LNS14000002, line = list(color = 'rgb(255, 0, 0)'))%>%
  layout(showlegend = F, title='Unemployement Rate for Women in U.S.A during the 2000\'s',
         xaxis = list(rangeslider = list(visible = T)))

fig <- fig %>%
  layout(
         xaxis = list(zerolinecolor = '#ffff',
                      zerolinewidth = 2,
                      gridcolor = 'ffff', 
                      title = 'Time'),
         yaxis = list(zerolinecolor = '#ffff',
                      zerolinewidth = 2,
                      gridcolor = 'ffff', 
                      title = 'Unemployement Rate'),
         plot_bgcolor='#e5ecf6', width = 900)

fig

```